---
title: "The linreg package"
author: "Henrik Olofsson and Sofie Jörgensen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The linreg package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```




```{r}
library(linreg)
```


This vignette is a documentation of how to use the `linreg` package. 
For this purpose, we will use the `mtcars` data set.



```{r}
usethis::use_vignette("my-vignette")
data(mtcars)
head(mtcars)
```


# Fitting a Linear Regression Model
We use the `mtcars` data set to fit a linear regression model. In this example, we are interested to 
investigate the impact of weight (1000 lbs) and number of cylinders on 
Miles/(US) gallon, for cars in the `mtcars` data set. Thus, the independent
variables are `wt` and `cyl` and the dependent variable is `mpg`,
and can be expressed as $\text{mpg} \sim \text{wt} + \text{cyl}$.

A linear regression model is fitted by using the linreg function, which returns an object of an S3 class. 

```{r}
model <- linreg(formula = mpg ~ wt + cyl, data = mtcars, QR = TRUE)
```


The `linreg` function calculates the coefficient estimates as well as the variance of the estimates using QR decomposition if `QR = TRUE`, otherwise the estimates are calculated using ordinary least squares.

# Methods

The following methods are able to take an object of class `linreg` as an argument: `print()`, `plot()`, `resid()`, `pred()`, `coef()` and `summary()`

Let us begin by printing the `model`object using the `print()` method, which returns the argument and the estimates of the coefficient.

```{r}
print(model)
```


Now let us visualize some diagnostics for the `linreg` object. The `plot()` method returns two plots with the graphical profile of Linköping University: a plot of residuals against fitted values and a Scale-Location plot of the standardized residuals against fitted values. 


```{r, message=FALSE}
plot(model)
```


Further, we can extract the model residuals from the `linreg` object and get the coefficients by using `resid()`and `coef()`, respectively. 


```{r}
resid(model)

coef(model)
```


To get a nice overview, we can summarize the linear model fit with `summary()`.


```{r}
summary(model)
```











