---
title: "The ridgereg function in the linreg package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ridgereg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
library(caret)
library(mlbench)
```

The updated version of the `linreg` package provides a new function called `ridgereg()` that performs ridge regression. We are delighted to present the `ridgereg` function in this vignette and now we will show its functionality by an example. In the following example, we will create a predictive model for the `BostonHousing` data in the `mlbench` package. For the model training process we will use the `caret` package. Both packages are loaded in our workspace. 

Now let's get started! 

First, the `BostonHousing` data will be divided into a training set and a test set by using the
`caret` package, where $80\%$ will be for training, and the remaining $20\%$ for testing. The response variable is `medv` (median value of owner-occupied homes in USD 1000's).

```{r}
data("BostonHousing")
set.seed(123)
trainIndex <- createDataPartition(BostonHousing$medv, p = .8, 
                                  list = FALSE, 
                                  times = 1)
train_data <- BostonHousing[ trainIndex,]
test_data  <- BostonHousing[-trainIndex,]
```
After dividing the data into a training and a test set, we will now fit two linear regression models to the `BostonHousing` training data using the `caret` package - one model consists of all continuous variables as predictors, and one model with only significant continuous variables using forward selection. Another package called `leaps` is required in order to perform forward selection. 

```{r}

library(leaps)
# Linear regression
lin <- train(medv ~ ., data = train_data, 
                 method = "lm")

# Linear Regression with Forward Selection
lin_forward <- train(medv ~ ., data = train_data, 
                 method = "leapForward")
```



