---
title: "The ridgereg function in the linreg package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ridgereg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
library(caret)
library(mlbench)
```

The updated version of the `linreg` package provides a new function called `ridgereg()` that performs ridge regression. We are delighted to present the `ridgereg` function in this vignette and now we will show its functionality by an example. In the following example, we will create a predictive model for the `BostonHousing` data in the `mlbench` package. For the model training process we will use the `caret` package. Both packages are loaded in our workspace. 

Now let's get started! 

First, the `BostonHousing` data will be divided into a training set and a test set by using the
`caret` package, where $80\%$ will be for training, and the remaining $20\%$ for testing. The response variable is `medv` (median value of owner-occupied homes in USD 1000's).

```{r}
data("BostonHousing")
set.seed(123)
trainIndex <- createDataPartition(BostonHousing$medv, p = .8, 
                                  list = FALSE, 
                                  times = 1)
BostonHousing_train <- BostonHousing[ trainIndex,]
BostonHousing_test  <- BostonHousing[-trainIndex,]
```
After dividing the data into a training and a test set, we will now fit a linear regression model. Two linear regression models will be fitted to the `BostonHousing` training data; one model consists of all predictor variables, and one model with only significant predictors to the fit using forward selection. 

Information on linear regression models in the caret package can be found here http://topepo.github.io/caret/Linear Regression.html.